A Spectral Analysis of the Domain Decomposed Monte Carlo Method for Linear Systems

### 2015-02-09 doc/ned2015/slattery_wilson_evans.tex
updating ned draft

%%---------------------------------------------------------------------------%%
\section{Acknowledgments}
This material is based upon work supported by the U.S. Department of
Energy, Office of Science, Advanced Scientific Computing Research
program.

This work was performed under appointment to the Nuclear Regulatory
Commission Fellowship program at the University of Wisconsin - Madison
Engineering Physics Department.

>>>>

%%---------------------------------------------------------------------------%%
\section{Acknowledgments}
This work was performed under appointment to the Nuclear Regulatory
Commission Fellowship program at the University of Wisconsin - Madison
Engineering Physics Department.

This material is based upon work supported by the U.S. Department of
Energy, Office of Science, Advanced Scientific Computing Research
program.
